PANNEURO_analysis

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd

```{ESS row sums r}
dat.raw <- dat.raw %>%
  mutate(ess.col.names =
   rowSums(select(.,als.col.names), na.rm = F)
   )
```

@@

>>>>

```{ESS row sums r}
dat.raw <- dat.raw %>%
  mutate(ess.col.names =
   rowSums(select(.,ess.col.names), na.rm = F)
   )
```

@@

## CFS

```{r}
cfs.col.names <- dat.raw %>%
  select(
    starts_with("cfs") & ends_with("numeric")
  ) %>%
  colnames()
cfs.col.names
```
```{r}
dat.raw <- dat.raw %>%
  mutate(cfs.sum_score =
   rowSums(select(.,cfs.col.names), na.rm = F) - 11
   )
cfs.col.names.physio <- cfs.col.names[1:7]

dat.raw <- dat.raw <- dat.raw %>%
  mutate(cfs.sum_score_physical=
   rowSums(select(.,cfs.col.names.physio), na.rm = F) - 7
   )

cfs.col.names.psych <- cfs.col.names[8:11]

dat.raw <- dat.raw <- dat.raw %>%
  mutate(cfs.sum_score_psyhchological =
   rowSums(select(.,cfs.col.names.psych), na.rm = F) -4
   )
```

```{r}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(cfs.sum_score)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  summarise(mean_total = mean(cfs.sum_score, na.rm = TRUE),
            mean_physical = mean(cfs.sum_score_physical, na.rm = TRUE),
            mean_psychological = mean (cfs.sum_score_psyhchological, na.rm = TRUE))

```{r}
dat.raw$cfs.correct_word_find_difficult_binary <- if_else(dat.raw$cfs.correct_word_find_difficult_numeric >= 3, 1,0)
dat.raw$cfs.do_you_have_problems_with_tiredness_binary<- if_else(dat.raw$cfs.do_you_have_problems_with_tiredness_numeric >= 3, 1,0)
dat.raw$cfs.do_you_feel_sleepy_or_drowsy_binary <- if_else(dat.raw$cfs.do_you_feel_sleepy_or_drowsy_numeric >= 3, 1,0)
dat.raw$cfs.do_you_feel_weak_binary <- if_else(dat.raw$cfs.do_you_feel_weak_numeric >= 3, 1,0)
dat.raw$cfs.do_you_have_difficulty_concentrating_binary <- if_else(dat.raw$cfs.do_you_have_difficulty_concentrating_numeric >= 3, 1,0)
dat.raw$cfs.do_you_have_problems_starting_things_binary <- if_else(dat.raw$cfs.do_you_have_problems_starting_things_numeric >= 3, 1,0)
dat.raw$cfs.do_you_lack_energy_binary <- if_else(dat.raw$cfs.do_you_lack_energy_numeric >= 3, 1,0)
dat.raw$cfs.do_you_need_to_rest_more_binary <- if_else(dat.raw$cfs.do_you_need_to_rest_more_numeric >= 3, 1,0)
dat.raw$cfs.how_is_your_memory_numeric_binary <- if_else(dat.raw$cfs.how_is_your_memory_numeric >= 3, 1,0) 
dat.raw$cfs.make_slips_speaking_tongue_binary <- if_else(dat.raw$cfs.make_slips_speaking_tongue_numeric >= 3, 1,0)
dat.raw$cfs.strength_muscles_binary <- if_else(dat.raw$cfs.strength_muscles_numeric >= 3, 1,0)
```

```{r}
cfs.col.names.bi <- dat.raw %>%
  select(
    starts_with("cfs") & ends_with("binary")
  ) %>%
  colnames()
cfs.col.names.bi
```
```{r}
dat.raw <- dat.raw %>%
  mutate(cfs.sum_score_binary =
   rowSums(select(.,cfs.col.names.bi), na.rm = F) 
   )

dat.raw <- dat.raw %>%
  mutate(cfs.sum_score_case = if_else(cfs.sum_score_binary >= 4, "Fatigue", "No fatigue"))

```{r}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(cfs.sum_score_case)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, cfs.sum_score_case) %>%
  mutate(Prop = round(n/sum(n), 2))
```
